### 2010-07-10 ms/titelblatt.tex
documentation updated

\vspace*{-2.8cm}
\begin{minipage}[c]{.30\textwidth}
  \begin{flushleft}
    \includegraphics[width=3cm,clip=]{LOGO/new-aerlogo.eps}%
  \end{flushleft}
\end{minipage}
\begin{minipage}[c]{.43\textwidth}
    { ~\\ Lehrstuhl f\"{u}r Aerodynamik \\ Prof.~Dr.-Ing. N.~A.~Adams}%
\end{minipage}
\begin{minipage}[c]{.25\textwidth}
  \begin{flushright}
    \vspace*{1em}
    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB.eps}%
  \end{flushright}
\end{minipage}

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
A Riemann solver }
\end{minipage}

\vspace*{0.8cm}
Mark F\"{o}rster\\

@@

\vspace*{1.2cm}
%\large
\normalsize
\vfill
\begin{tabular}{ll}
Betreuer: &  Dr.-Ing. Christian Stemmer \\
\ & \ \\
Ausgabe: & 1.\ Oktober 2008\\
Abgabe: & 31.\ M\"{a}rz 2009\\
\end{tabular}

\vspace*{1.6cm}
%\large
Lehrstuhl f\"{u}r Aerodynamik an der Technischen Universit\"{a}t M\"{u}nchen\\
2009
\end{center}

>>>>

\vspace*{-2.8cm}
\begin{minipage}[c]{.30\textwidth}
  \begin{flushleft}
    \includegraphics[width=3cm,clip=]{LOGO/new-aerlogo.eps}%
  \end{flushleft}
\end{minipage}
\begin{minipage}[c]{.43\textwidth}
    { ~\\ Institute of Aerodynamics \\ Prof.~Dr.-Ing. N.~A.~Adams}%
\end{minipage}
\begin{minipage}[c]{.25\textwidth}
  \begin{flushright}
    \vspace*{1em}
    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB.eps}%
  \end{flushright}
\end{minipage}

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
Simuation of a high enthalpy flow through porosities using SPH}
\end{minipage}

\vspace*{0.8cm}
Oliver Oberinger\\

@@

\vspace*{1.2cm}
%\large
\normalsize
\vfill
\begin{tabular}{ll}
Betreuer: &  Dipl.-Ing. Sergey Litvinov \\
\ & \ \\
Ausgabe: & 15.\ Juni 2010\\
Abgabe: & 15.\ Dezember 2010\\
\end{tabular}

\vspace*{1.6cm}
%\large
Institute of Aerodynamics Technische Universit\"{a}t M\"{u}nchen\\
Graduate Aerospace Laboratories California Institute of Technology
2010	
\end{center}
